Approximation as Differentiation: Notes

### 2025-06-03 notes/language.tex
Tweaks.

\figref{default-semantics:types} gives the default interpretation of types $\Delta \vdash \tau$ with
$\length{\Delta} = n$ as functors $\cat{C}^n \to \cat{C}$ (or as objects of $\cat{C}$ in the case $n = 0$).
\figref{default-semantics:terms} gives the default interpretation of terms $\Gamma \vdash t: \tau$ as
morphisms $\sem{\Gamma} \to \sem{\tau}$.

>>>>

\figref{default-semantics:types} gives the interpretation of types $\Delta \vdash \tau$ with $\length{\Delta}
= n$ as functors $\cat{C}^n \to \cat{C}$, or as objects of $\cat{C}$ in the case $n = 0$.
\figref{default-semantics:terms} gives the interpretation of terms $\Gamma \vdash t: \tau$ as morphisms
$\sem{\Gamma} \to \sem{\tau}$.
